---
title: "Liquor Time Series Analysis"
author: "Sophie"
date: "9/15/2020"
output: html_document
---



```{r}
product_monthly = read.csv("product_monthly.csv")
store_monthly = read.csv("store_monthly.csv")
store_prod_monthly = read.csv("store_prod_monthly.csv")
```


```{r}
head(product_monthly)
dim(product_monthly)
```


Total volume trend
```{r}
ts_total <- ts(product_monthly$total, start=c(2012, 1), end=c(2020, 8), frequency=12)

plot(ts_total, type = 'l')#, grid.ticks.on='M')
```

Total volume seasonal decomposition 
```{r}
stl_total = stl(ts_total, s.window = "periodic")
plot(stl_total, main = "Total Volume Seasonal Decomposition")
```


```{r}
monthplot(ts_total)
library(forecast)
seasonplot(ts_total)
```



Auto arima forecast on total volume 

```{r}
ts_total_train = ts(product_monthly$total[1:78], start=c(2012, 1), end=c(2018, 6), frequency=12)
ts_total_test= ts(product_monthly$total[79:104], start=c(2018, 7), end=c(2020, 8), frequency=12)
```


```{r}
fit_total = auto.arima(ts_total_train , test = "adf", trace=T)
```


Forecast total volume
```{r}
plot(forecast(fit_total, h=26))
```

```{r}
plot(forecast(fit_total, h=26))
```


Evaluating Arima model on total volume 
```{r}

AR_total.mean <-forecast(fit_total,h=26)$mean
plot(ts_total_test, main="ARIMA Forecast vs. Actual on Total Volume 2018-07 - 2020-08", ylab="", xlab="Months", col="darkblue")  
lines(AR_total.mean, col="red")
```

```{r}
fit_total_forecast <-forecast(fit_total,h=26)
accuracy(fit_total_forecast,ts_total_test)
```





Whisky trend
```{r}

ts_whisky <- ts(product_monthly$whisky, start=c(2012, 1), end=c(2020, 8), frequency=12)
stl_whisky = stl(ts_whisky, s.window = "periodic")

plot(ts_whisky, type = 'l')#, grid.ticks.on='M')
```


Whisky Seasonal decomposition 

```{r}
stl_whisky = stl(ts_whisky, s.window = "periodic")
plot(stl_whisky)
```


ACF test
```{r}
acf(ts_whisky, lag.max = 100)
pacf(ts_whisky, lag.max = 100)
```


Choosing the beginning 75% of the monthly data (78 months) as training, remaining 25% as test
```{r}
ts_whisky_train = ts(product_monthly$whisky[1:78], start=c(2012, 1), end=c(2018, 6), frequency=12)
ts_whisky_test= ts(product_monthly$whisky[79:104], start=c(2018, 7), end=c(2020, 8), frequency=12)
```


```{r}
fit1 = auto.arima(ts_whisky_train , test = "adf", trace=T)
```

Auto Arima result with adf test
```{r}
summary(fit1)
checkresiduals(fit1)
```

```{r}
qqnorm(fit1$residuals)
```


Forecast fit1
```{r}
plot(forecast(fit1, h=26))
```

```{r}
# plot of the test set and its prediction only

AR.mean <-forecast(fit1,h=26)$mean
plot(ts_whisky_test, main="ARIMA Forecast on Whisky Volume 2018-07 - 2020-08", ylab="", xlab="Months", col="darkblue")  
lines(AR.mean, col="red")
```

```{r}
fit1_forecast <-forecast(fit1,h=26)
accuracy(fit1_forecast,ts_whisky_test)
```



Supermarket - Whisky 


```{r}
ts_sw <- ts(store_prod_monthly$Supermarketwhisky, start=c(2012, 1), end=c(2020, 8), frequency=12)
stl_sw = stl(ts_sw, s.window = "periodic")
plot(ts_sw, type = 'l')#, grid.ticks.on='M')
plot(stl_sw)

```

```{r}
ts_sw_train = ts(store_prod_monthly$Supermarketwhisky[1:78], start=c(2012, 1), end=c(2018, 6), frequency=12)
ts_sw_test= ts(store_prod_monthly$Supermarketwhisky[79:104], start=c(2018, 7), end=c(2020, 8), frequency=12)

```



```{r}
fit_sw = auto.arima(ts_sw_train, test = "adf", trace=T)
summary(fit_sw)
checkresiduals(fit_sw)
qqnorm(fit_sw$residuals)
```

```{r}
plot(forecast(fit_sw, h=30))
```

```{r}
forecast(fit_sw, h=30)
```

```{r}
575372.6 / 360
```


```{r}
AR.mean.sw <-forecast(fit_sw,h=26)$mean
plot(ts_sw_test, main="ARIMA Forecast on Supermarket Whisky Volume 2018-07 - 2020-08", ylab="", xlab="Months", col="darkblue")  
lines(AR.mean.sw, col="red")

```

```{r}
fit_sw_forecast <-forecast(fit_sw,h=26)
accuracy(fit_sw_forecast,ts_sw_test)
```



Supermarket + Vodka 
```{r}
ts_sv <- ts(store_prod_monthly$Supermarketvodka, start=c(2012, 1), end=c(2020, 8), frequency=12)
ts_sv_train = ts(store_prod_monthly$Supermarketvodka[1:78], start=c(2012, 1), end=c(2018, 6), frequency=12)
ts_sv_test= ts(store_prod_monthly$Supermarketvodka[79:104], start=c(2018, 7), end=c(2020, 8), frequency=12)

```


```{r}
fit_sv = auto.arima(ts_sv_train, test = "adf", trace=T)
summary(fit_sv)
checkresiduals(fit_sv)
qqnorm(fit_sv$residuals)
```

```{r}
AR.mean.sv <-forecast(fit_sv,h=26)$mean
plot(ts_sv_test, main="ARIMA Forecast on Supermarket Whisky Volume 2018-07 - 2020-08", ylab="", xlab="Months", col="darkblue")  
lines(AR.mean.sv, col="red")
```

```{r}
fit_sv_forecast <-forecast(fit_sv,h=26)
accuracy(fit_sv_forecast,ts_sv_test)
```







Store type 
```{r}
head(store_monthly)

ts_supermarket = ts(store_monthly$Supermarket, start=c(2012, 1), end=c(2020, 8), frequency=12)
ts_conv = ts(store_monthly$Convenience.Store, start=c(2012, 1), end=c(2020, 8), frequency=12)
ts_liquor = ts(store_monthly$Liquor.Tobacco.Store, start=c(2012, 1), end=c(2020, 8), frequency=12)
plot(ts_supermarket, type = "l")
plot(ts_conv, type = "l")
plot(ts_liquor, type = "l")
```





































